Supporting Information:\\Black-swan events in animal populations

### 2016-05-27 text/ms.tex
Adjust keywords
Add back overview 2tto methods

Keywords:
Bayesian,
black swans,
die-offs,
ecological surprises,
heavy tails,
Gompertz,
mass mortality,
population dynamics,
risk,
Student t

@@

>>>>

Keywords:
Bayesian,
die-offs,
ecological surprises,
Gompertz,
heavy tails,
leptokurtic,
mass mortality,
population dynamics,
risk,
Student t

@@

We fit population dynamics models in which the process noise is
drawn from a Student-t distribution. By estimating the degrees of freedom
parameter, \(\nu\), we can estimate the degree to which the process deviations
have heavy tails and are therefore diagnostic of black-swan events (Fig.~1,
fig.~S\ref{fig:priors}). Lower values of \(\nu\) result in heavy-tailed
distributions.
% For example, at \(\nu = 2\), an event
% more than 4 standard deviations below the mean is expected
For example, an event four standard deviations below the mean
is expected to happen once every 35 years with a t distribution with \(\nu = 2\)
compared to once every 32,000 years with a normal distribution
% more than four standard deviations below the mean is almost 70,000 times higher
% than the probability of drawing such a value from a normal distribution
% (\(0.02\) vs.\ \(2.9\cdot10^{-7}\)).
As \(\nu\) approaches infinity, the t
distribution approaches the normal distribution (Fig.~1).
